---
title: "TidyTemplate"
date: 2021-02-24
output: html_output
---

# TidyTuesday

Following David Robinson's YouTube video on this TidyTuesday dataset.

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_light(18))

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-02-23")

earn <- tt$earn
employed <- tt$employed %>% 
  mutate(dimension = case_when(
    race_gender == "TOTAL" ~ "Total",
    race_gender %in% c("Men", "Women") ~ "Gender",
    TRUE ~ "Race"))

```

Work on the plot.
``` {r Work}
employed %>% 
  filter(dimension == "Total") %>% 
  filter(!is.na(employ_n)) %>% 
  mutate(industry = fct_lump(industry, 8, w = employ_n),
         industry = fct_reorder(industry, employ_n, sum)) %>% 
  ggplot(aes(year, employ_n, fill = industry))+
  geom_col()+
  scale_y_continuous(labels = comma)+
  labs(y = "# employed")
  
```

```{r}

```

# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}



```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
