---
title: "TidyTemplate"
date: 2021-02-24
output: html_output
---

# TidyTuesday

Following David Robinson's YouTube video on this TidyTuesday dataset.

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_light(18))

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2021-02-23")

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```


# Get sub data

```{r} 
earn <- tt$earn
employed <- tt$employed %>% 
  mutate(dimension = case_when(
    race_gender == "TOTAL" ~ "Total",
    race_gender %in% c("Men", "Women") ~ "Gender",
    TRUE ~ "Race"))
```


# Wrangle and plot
``` {r Work}
employed_clean <-
  employed %>% 
  filter(!is.na(employ_n)) %>% 
  mutate(industry = fct_lump(industry, 8, w = employ_n),
         industry = fct_reorder(industry, employ_n, sum)) %>% 
  identity()

employed_clean %>% 
  filter(dimension == "Total") %>% 
  ggplot(aes(year, employ_n, fill = industry))+
  geom_col()+
  scale_y_continuous(labels = comma)+
  labs(y = "# employed")

employed_clean %>% 
  filter(dimension == "Gender") %>% 
  group_by(industry, year, race_gender) %>% 
  summarize(employ_n = sum(employ_n)) %>% 
  ggplot(aes(year, employ_n, color = race_gender))+
  geom_line()+
  facet_wrap( ~ industry, scales = "free_y")+
  expand_limits(y = 0)+
  scale_y_continuous(labels = comma)+
  labs(y = "# employed",
       color = "Gender")

employed_clean %>% 
  filter(year == 2020,
         industry == "Leisure and hospitality") %>% 
  View()
  
```

Focus on 2019-2020
```{r}
industry_2019_2020 <-
  employed_clean %>% 
  filter(year %in%  c(2019, 2020)) %>% 
  group_by(year, industry, dimension, race_gender) %>% 
  summarize(employ_n = sum(employ_n))

industry_2019_2020 %>% 
  filter(dimension == "Total") %>% 
  mutate(industry = fct_reorder(industry, employ_n, sum)) %>% 
  ggplot(aes(year, employ_n, color = industry))+
  geom_line()+
  scale_x_continuous(breaks = 2019:2020)+
  scale_color_discrete(guide = guide_legend(reverse =TRUE))+
  expand_limits(y = 0)+
  scale_y_continuous(labels = comma)


```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.

```{r Readme, eval = interactive()}

tt

```


# Save Image

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
