---
title: "Coffee ratings"
author: Sahra Uygun
date: 2021-06-08
output: html_output
---


Following: https://github.com/rstats-aficionadas/guidedTidyTuesday
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(tidytuesdayR)
# library(skimr)

```

# Load the coffee ratings data from July-2020

```{r Load, include=FALSE}

tt <- tt_load("2020-07-07")

```

# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Read and explore options

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r read, include=FALSE}

coffee <- tt$coffee_ratings
# summary(coffee)
# names(coffee)
# str(coffee)
# head(coffee)
# glimpse(coffee)
skimr::skim(coffee)

```

Some things to consider:

* missing data
* data types
* messy/tidy data
* R reads mostly as character can be converted to factor


```{r Wrangle, include=FALSE}

# coffee %>% 
#   mutate(species = as_factor(species),
#          country_of_origin = as_factor(country_of_origin))

coffee <- coffee %>% 
  mutate(across(c(country_of_origin, species), as_factor))

```


# Plots

Cup points by altitude

* total_cup_points
* altitude_mean_meters

Does coffee grown in higher/lower regions taste better/have better ratings?


```{r Visualize}

coffee %>% 
  filter(altitude_mean_meters < 5000 & total_cup_points > 50) %>%
  ggplot() +
  aes(x = altitude_mean_meters, y = total_cup_points,
      colour = species) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "average altitude in metres",
       y = "total cup points",
       title = "Total cup points by altitude and coffee species",
       subtitle = 'I <3 coffee',
       caption = "Data source: Tidy Tuesday")

  
```

## Cup points by country

```{r}
coffee %>% 
  filter(altitude_mean_meters < 5000 & total_cup_points > 50) %>% 
  ggplot() +
  aes(x = altitude_mean_meters, y = total_cup_points,
      colour = country_of_origin) +
  geom_point() +
  #geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "average altitude in metres",
       y = "total cup points",
       title = "Total cup points by altitude and country of origin",
       subtitle = 'I <3 coffee',
       caption = "Data source: Tidy Tuesday")
```

```{r}
summary(coffee$country_of_origin)
coffee %>% 
  count(country_of_origin) %>% 
  arrange(desc(n))
```

```{r}
coffee %>% 
  filter(country_of_origin %in% c("Mexico", "Colombia", "Guatemala", "Brazil")) %>% 
  filter(altitude_mean_meters < 5000 & total_cup_points > 50) %>% 
  ggplot() +
  aes(x = altitude_mean_meters, y = total_cup_points,
      colour = country_of_origin) +
  geom_point() +
  #geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "average altitude in metres",
       y = "total cup points",
       title = "Total cup points by altitude and country of origin",
       subtitle = 'I <3 coffee',
       caption = "Data source: Tidy Tuesday",
       colour = "country of origin")
```



```{r}
coffee %>% 
  add_count(country_of_origin, name = "country_n") %>% 
  filter(country_n > 100 & altitude_mean_meters < 5000 & total_cup_points > 50) %>% 
  ggplot() +
  aes(x = altitude_mean_meters, y = total_cup_points,
      colour = country_of_origin) +
  geom_point() +
  #geom_smooth(method = "lm") +
  theme_minimal() +
  labs(x = "average altitude in metres",
       y = "total cup points",
       title = "Total cup points by altitude and country of origin",
       subtitle = 'I <3 coffee',
       caption = "Data source: Tidy Tuesday",
       colour = "country of origin") 
coffee %>% 
  add_count(country_of_origin, name = "country_n") %>% 
  select(country_of_origin, country_n) %>% 
  distinct()
```

## Histograms/density plots

```{r}
coffee %>% 
  ggplot() +
  aes(x = aroma, colour = species, fill = species) +
  geom_density(alpha = 0.3) +
  theme_light() +
  labs(title = "Aroma by coffee species") +
  scale_fill_manual(values = c("seagreen", "steelblue")) +
  scale_colour_manual(values = c("seagreen", "steelblue"))
```

## Boxplot

```{r}
ggplot(coffee) +
  aes(x = species, y = sweetness,
      colour = species) +
  geom_violin() +
  geom_boxplot(width = 0.3) +
  geom_jitter(alpha = 0.4) +
  theme_light() +
  theme(legend.position = "bottom")
```
